A Novel Approach to Supervised Classification Using Non-Linear Metrics

### 2017-01-24 icml2017/paper.tex
add

\includegraphics[scale=.1]{fig/c5.eps}
\includegraphics[scale=.1]{fig/c6.eps}
\includegraphics[scale=.1]{fig/c12.eps}

outlier
\includegraphics[scale=.1]{fig/c7.eps}

\includegraphics[scale=.1]{fig/c8.eps}
\includegraphics[scale=.1]{fig/c10.eps}

\includegraphics[scale=.1]{fig/MNIST119.eps}
\includegraphics[scale=.1]{fig/MNIST121.eps}
\includegraphics[scale=.1]{fig/MNIST122.eps}
\includegraphics[scale=.1]{fig/MNIST124.eps}

ourlier
\includegraphics[scale=.1]{fig/MNIST120.eps}

>>>>

\subsection{MNIST}

following table shows the outlier (first column) and 3 closest points in the dataset

\begin{tabular}{cccc}

2 &1& 1& 1\\

\includegraphics[scale=.1]{fig/MNIST_207_2_0_207_2.eps}&
\includegraphics[scale=.1]{fig/MNIST_207_2_1_942_1.eps}&
\includegraphics[scale=.1]{fig/MNIST_207_2_2_510_1.eps}&
\includegraphics[scale=.1]{fig/MNIST_207_2_3_514_1.eps}

\\ \hline 
2 & 0 & 2 & 2\\
\includegraphics[scale=.1]{fig/MNIST_392_2_0_392_2.eps} &
\includegraphics[scale=.1]{fig/MNIST_392_2_1_161_0.eps}&
\includegraphics[scale=.1]{fig/MNIST_392_2_2_424_2.eps}&
\includegraphics[scale=.1]{fig/MNIST_392_2_3_609_2.eps}
\\
\hline 
2 & 0 & 0 & 0 \\

\includegraphics[scale=.1]{fig/MNIST_653_2_0_653_2.eps} &
\includegraphics[scale=.1]{fig/MNIST_653_2_1_171_0.eps}&
\includegraphics[scale=.1]{fig/MNIST_653_2_2_252_0.eps}&
\includegraphics[scale=.1]{fig/MNIST_653_2_3_938_0.eps}

\\
\hline 
2 & 0 & 0 & 0 \\

\includegraphics[scale=.1]{fig/MNIST_771_2_0_771_2.eps} &
\includegraphics[scale=.1]{fig/MNIST_771_2_1_818_0.eps} &
\includegraphics[scale=.1]{fig/MNIST_771_2_2_875_0.eps} &
\includegraphics[scale=.1]{fig/MNIST_771_2_3_793_0.eps}

\\ \hline

1 & 2 & 2 &2 \\

\includegraphics[scale=.1]{fig/MNIST_947_1_0_947_1.eps}&
\includegraphics[scale=.1]{fig/MNIST_947_1_1_913_2.eps}&
\includegraphics[scale=.1]{fig/MNIST_947_1_2_806_2.eps}&
\includegraphics[scale=.1]{fig/MNIST_947_1_3_13_2.eps}
\\ \hline
1 & 2 & 1 & 2 \\

\includegraphics[scale=.1]{fig/MNIST_962_1_0_962_1.eps}&
\includegraphics[scale=.1]{fig/MNIST_962_1_1_760_2.eps}&
\includegraphics[scale=.1]{fig/MNIST_962_1_2_733_1.eps}&
\includegraphics[scale=.1]{fig/MNIST_962_1_3_456_2.eps}

\end{tabular}

\clearpage
\subsection{Experiments with synthetic data}

We compare with LMNN (I used the lmnn v3 software)
with our approach
In Figure \ref{fig:synthetic} we show the dataset
and also we show the unit distance plot for various $K$ for LMNN algorithm.
Note that for value of $K=2$ and $K=4$ the their result is terrible.
\begin{figure}[h!]

\includegraphics[scale=.2]{fig/synthetic1.eps}
\includegraphics[scale=.3]{fig/synthetic1lmnn.eps}
\includegraphics[scale=.2]{fig/synthetic1our.eps}

\caption{Comparison of LMNN for various parameter $K$.
In code it is written 
 attract $K$ nearest similar labeled vectors. 
 The last plot on right is the solution give by our algorithm. 
 PS: just to note, this is different from the one you are used to plot.
}
\label{fig:synthetic}
\end{figure}
